Extended Data

### 2022-03-14 doc/manuscript/Dow_manuscript_Nature.Rmd
#92

In recent decades, tree growth in Earth's forests has more than offset losses from deforestation and other disturbances, such that a net forest CO~2~ sink of ~`r round(5.8*12/44,1)` Gt C yr^-1^<!--net forest estimate in Harris et al. Table 2--> offsets ~`r round(5.8/32,1)*100`%<!--net forest estimate / fossil fuel & cement, (Harris et al. Table 2)--> of anthropogenic emissions[@harris_global_2021], dramatically slowing the pace of atmospheric CO~2~ accumulation and climate change.
Of this important C sink, ~`r round(3.6/7.6,2)*100`%<!-- temperate net / global net, (Harris et al. Table 1)--> occurs in temperate forests[@harris_global_2021], with temperate deciduous forests sequestering >0.3 Gt C yr^-1^ [@pugh_role_2019]. <!-- Pugh et al. 2019 estimate that the temperate deciduous sink is >300 Tg C yr-1, with ~200 Tg C yr-1  attributable to demography (forest regrowth) and >100 Tg C yr-1  controlled by environmental drivers.--> 
The future behavior of this C sink will play an important yet uncertain role in influencing atmospheric CO~2~ and climate change[@arora_carbon_2020;@friedlingstein_global_2020;@fatichi_moving_2014].

>>>>

In recent decades, tree growth in Earth's forests has more than offset losses from deforestation and other disturbances, such that a net forest CO~2~ sink of ~`r round(5.8*12/44,1)` Gt C yr^-1^<!--net forest estimate in Harris et al. Table 2--> offsets ~`r round(5.8/32,1)*100`%<!--net forest estimate / fossil fuel & cement, (Harris et al. Table 2)--> of anthropogenic emissions[@harris_global_2021], dramatically slowing the pace of atmospheric CO~2~ accumulation and climate change.
<!--@xu_changes_2021 provides an alternate estimate, which is about half of Harris. The main difference being that Xu includes savannas and woodlands, which have experienced a lot of loss from fires. Given focus on forests here, Harris seems more appropriate. -->
Of this important C sink, ~ `r round(3.6/7.6,2)*100`%<!-- temperate net / global net, (Harris et al. Table 1)--> occurs in temperate forests[@harris_global_2021],
<!-- alternate estimate: `r round(.31/.88,2)*100`% (temperate net / global net, (@xu_changes_2021. Table 2))--> 
with temperate deciduous forests sequestering >0.3 Gt C yr^-1^ [@pugh_role_2019]. <!-- Pugh et al. 2019 estimate that the temperate deciduous sink is >300 Tg C yr-1, with ~200 Tg C yr-1  attributable to demography (forest regrowth) and >100 Tg C yr-1  controlled by environmental drivers.--> 
The future behavior of this C sink will play an important yet uncertain role in influencing atmospheric CO~2~ and climate change[@arora_carbon_2020;@friedlingstein_global_2020;@fatichi_moving_2014].
